### 2023-02-26 manuscript.tex
Minor edits to the letter [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/040e70b2b68ac8822e659081c5404a1ed8afe972.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/040e70b2b68ac8822e659081c5404a1ed8afe972/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4276944252

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/371f6f710b0016df19bf0858b534ba45cc4c2505/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/371f6f710b0016df19bf0858b534ba45cc4c2505}{SORTEE-Github-Hackathon/manuscript@371f6f7}
on February 26, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/040e70b2b68ac8822e659081c5404a1ed8afe972/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/040e70b2b68ac8822e659081c5404a1ed8afe972}{SORTEE-Github-Hackathon/manuscript@040e70b}
on February 26, 2023.
